WIP: Transparent Standby for Low-Power, Resource-Constrained Embedded Systems

### 2018-02-17 LCTES/lctes.tex
(>) add WIP tag
(>) ACM conference

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

@@

\begin{document}
%\title{A Language-Based Approach for Standby in Embedded Systems}
\title{Transparent Standby for Low-Power, Resource-Constrained Embedded Systems}
\subtitle{A Programming Language-Based Approach}

>>>>

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El Paso, Texas USA}
\acmConference[LCTES'18]{ACM SIGPLAN/SIGBED}{June 2018}{Philadelphia, Pennsylvania, USA}
%\acmYear{1997}
%\copyrightyear{2016}

%\acmPrice{15.00}

@@

\begin{document}
%\title{A Language-Based Approach for Standby in Embedded Systems}
\title{WIP: Transparent Standby for Low-Power, Resource-Constrained Embedded Systems}
\subtitle{A Programming Language-Based Approach}
